Component-based Software Development Framework \\for Embedded IoT Devices（仮）

### 2017-11-08 ipsj/paper.tex
Update System Model

{\bf Organization}: The remainder of this paper is organized as follows.
Section \ref{sec:System Model} introduces the system model of the proposed framework and the basic technologies, i.e., mruby, TECS, and mruby on TECS.
Section \ref{sec:Proposed Framework} describes the design and implementation of the proposed framework, including TINET+TECS and TLSF+TECS.
Section \ref{sec:Evaluation} evaluates the proposed framework.
Related work is discussed in Section \ref{sec:Related Work}.
Conclusions and suggestions for future work are presented in Section \ref{sec:Conclusion}.

@@

The proposed framework is an extension of mruby on TECS framework \cite{par:mrubyonTECS}\cite{par:mrubyonTECS2}, and utilizes two technologies: mruby and TECS.
In this section, mruby (\ref{sec:mruby}), TECS (\ref{sec:TECS}), and mruby on TECS framework (\ref{sec:mrubyonTECS}) are described.

@@

@@

>>>>

{\bf Organization}: The remainder of this paper is organized as follows.
Section \ref{sec:System Model} introduces the system model of the proposed framework and the basic technologies, i.e., TECS, mruby, and mruby on TECS.
Section \ref{sec:Proposed Framework} describes the design and implementation of the proposed framework, including TINET+TECS and TLSF+TECS.
Section \ref{sec:Evaluation} evaluates the proposed framework.
Related work is discussed in Section \ref{sec:Related Work}.
Conclusions and suggestions for future work are presented in Section \ref{sec:Conclusion}.

@@

The proposed framework is an extension of mruby on TECS framework \cite{par:mrubyonTECS}\cite{par:mrubyonTECS2}, and utilizes two technologies: mruby and TECS.
In this section, TECS,  mruby, and mruby on TECS framework are described.

@@

mruby is a light-weight implementation of the Ruby programming language complying to part of the ISO standard.
Ruby is an object-oriented scripting language \cite{url:Ruby} with classes and methods, exceptions, and garbage collection functions.
It is easy to use and read due to its simple grammar and Ruby requires fewer lines of code than C.
Ruby improves the productivity of software development due to its simple grammar and object-oriented functions.

mruby, which retains the usability and readability of Ruby, requires fewer resources, and thus, is suitable for embedded systems.
In addition, mruby includes a VM mechanism, and thus, mruby programs can run on any operating system as long as a VM is implemented.
The mruby/RiteVM mechanism is shown in Fig.\ref{fig:mruby}.
The mruby compiler translates an mruby code into a bytecode, which can be interpreted by a RiteVM; thus, mruby programs can be executed on any target device with a RiteVM.

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/mruby.pdf}
    \caption{mruby/RiteVM mechanism}
    \label{fig:mruby}
\end{figure}

@@

mruby on TECS is a component-based framework for running an mruby script language on embedded systems.
This framework integrates two technologies, mruby and TECS, and enables to develop embedded software using a script language without slowing down the execution time.

\subsubsection{System Model of mruby on TECS}
The present mruby on TECS system model is shown in Fig.\ref{fig:mrubyontecs}.
Each mruby program, which is a bytecode, runs on its own RiteVM as a componentized task of an RTOS.
TECS components support various embedded drivers such as motor and sensor drivers.

An mruby-TECS bridge provides native libraries for mruby and can call a native program (e.g., C legacy code) from an mruby program.
The mruby-TECS bridge also provides TECS components for receiving the invocation from an mruby program.

In this paper, TOPPERS/ASP3 \cite{par:ASP}, \cite{url:ASP} is the target RTOS and is based on $\mu$ITRON \cite{par:microITRON} .
However, mruby on TECS does not depend on the RTOS because TECS supports not only TOPPERS/HRP2 but also the other RTOSs such as OSEK \cite{par:OSEK} and TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs}.

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/mrubyontecs.pdf}
\caption{System model of existing mruby on TECS}
\label{fig:mrubyontecs}
\end{figure}

\subsubsection{mruby-TECS Bridge}
There is a significant difference between the execution times of mruby and C language codes.
According to  \cite{par:mrubyonTECS}, mruby programs are several hundred times slower than C programs and the execution of an mruby bytecode on a RiteVM is not as efficient as that of C code.
Thus, it is difficult to use mruby exclusively.

Using Ruby on embedded devices improves productivity and maintainability because it is easy to use and read.
However, some C language codes are required to manipulate actuators and sensors and ensure that critical sections of the code run quickly.

Fig.\ref{fig:mrubyTECSbridge} illustrates an mruby-TECS bridge used to control a motor.
The left side of BridgeMotor belongs to the mruby program.
The right side of BridgeMotor belongs to TECS component.

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/mrubyTECSbridge.pdf}
\caption{mruby-TECS bridge}
\label{fig:mrubyTECSbridge}
\end{figure}

The mruby-TECS bridge generates a {\it celltype}, which is called from the mruby code, and an mruby class, which corresponds to a developer-specified TECS component to invoke a C function from the mruby program.

The generated mruby-TECS bridge supports registration of classes and methods for mruby.
Methods in an mruby class are defined by generation codes for an mruby-TECS bridge, such as setPower and stop.
Thus, when a method is called in an mruby program, the mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\it cell}.
